\documentclass{cmslatex}
\pdfoutput=1
\usepackage{pst-pdf}
\usepackage{amsmath,amsfonts}
\usepackage{subfigure}
\graphicspath{{./}{figs/}}
\usepackage{graphicx}
\usepackage{psfrag}
\usepackage{dcolumn}
\usepackage{rotating}
\usepackage{xspace}
\usepackage{url}
\usepackage{upgreek}
\usepackage{multicol}
\usepackage{pict2e,slashbox,multirow}
\usepackage{verbatim}
\usepackage[hmargin=1.0in]{geometry}
\usepackage{yhmath}
%\usepackage[integrals]{wasysym}


\begin{document}
\title{Shock Dynamics in Layered Periodic Media}

\author{%
  David I. Ketcheson\thanks{Mathematical and Computer Sciences Division, King Abdullah University of Science and
    Technology, 4700 KAUST, Thuwal 23955, Saudi Arabia.
   (\protect\url{david.ketcheson@kaust.edu.sa})} \and
    Randall J. LeVeque\thanks{Department of Applied Mathematics, University of Washington, Box 352420, Seattle, WA 98195-2420.
   (\mbox{rjl@uw.edu}) }}

\maketitle

\bibliographystyle{siam}

\begin{abstract}
Solutions of constant-coefficient nonlinear hyperbolic PDEs generically 
develop shocks, even if the initial data is smooth.  Solutions of hyperbolic
PDEs with variable coefficients can behave very differently.
We investigate formation and stability of shock waves in a one-dimensional 
periodic layered medium by computational study of time-reversibility and entropy 
evolution.
We find that periodic layered media tend to inhibit shock formation.
For small initial conditions and large impedance variation, 
no shock formation is detected even
after times much greater than the time of shock formation in a homogeneous
medium.  Furthermore, weak shocks are observed to be dynamically unstable in
the sense that they do not lead to significant long-term entropy decay.
%Stronger shocks are observed to travel at a modified 
%velocity related to what may be considered as effective jump conditions.
We propose a characteristic condition for admissibility of shocks in heterogeneous
media that generalizes the classical Lax entropy condition
and accurately predicts the formation or absence of shocks in these media.
\end{abstract}

\begin{keywords}
shock waves, periodic media, dispersive shocks, solitary waves
\smallskip

{\bf 35L02,35L67,74E15,65M08,37K40}
\end{keywords}


\pagestyle{myheadings}
\thispagestyle{plain}
\markboth{D. I. Ketcheson and R. J. LeVeque}{Shock dynamics in periodic media}
%============================================================
%Define macros, environments, etc.
\input{macros}
%============================================================

\section{Introduction\label{intro}}
\input{intro}

%\section{Effective Medium Description}
%  \input{homogenized}
%%  \subsection{Riemann invariants}
%%    \input{ri}

\section{Computational Measures of Shock Formation\label{measures}}
  \input{regularization}
  \subsection{Time Reversal}
    \input{timereversal}
  \subsection{Entropy Evolution}
    \input{entropy}

\section{A Condition for Shock Formation in Heterogeneous Media\label{criterion}}
    \input{criterion}

\section{Discussion\label{discussion}}
  \input{conclusions}

\bibliography{stego}

\end{document}
